---
title: "Mohamed El Saady's CV"
author: Mohamed El Saady
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['css/styles.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(glue)
library(tidyverse)



# Set this to true to have links turned into footnotes at the end of the document
PDF_EXPORT <- FALSE

# Holds all the links that were inserted for placement at the end
links <- c()

source('parsing_functions.R')

# Load csv with position info
position_data <- read_csv('positions.csv')
```


```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("
  <style>
  :root{
    --decorator-outer-offset-left: -6.5px;
  }
  </style>")
}
```


Aside
================================================================================



```{r}
# When in export mode the little dots are unaligned, so fix that. 
if(PDF_EXPORT){
  cat("View this CV online with links at _nickstrayer.me/cv_")
} else {
  cat("[<i class='fas fa-download'></i> Download a PDF of this CV](https://github.com/Mohamed-elsaady/cv/raw/master/Mohamed-El Saady’s-cv.pdf)")
}
```

Contact {#contact}
--------------------------------------------------------------------------------


- <i class="fa fa-envelope"></i> melsaady@asu.edu
- <i class="fa fa-github"></i> github.com/Mohamed-elsaady
- <i class="fa fa-phone"></i> (971) 507537818



Skills & Expertise {#skills}
--------------------------------------------------------------------------------

- • R programming
- • Data wrangling, Data visualization
- • Github
- • PHP
- • HTML5 & CSS3 BEM notation
- • Bootstrap, tailwind, Zurb Foundation
- • Flexbox Grid
- • Sass(scss), PostCSS
- • Wireframing and UX
- • Sketch, Illustrator, Figma
- • Javascript, OOP, DOM
- • ReactJS & Redux
- • Yarn, Gulp, Webpack, Parcel
- • Linux, Windows, GCP and AWS
- • Lamp Stack, Apache, Nginx, IIS 7.0

```{r}


```





Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Made with the R package [pagedown](https://github.com/rstudio/pagedown). 

The source code is available at <br/> [github.com/Mohamed-elsaady/cv](https://github.com/Mohamed-elsaady).




Main
================================================================================

Mohamed El Saady {#title}
--------------------------------------------------------------------------------


```{r}
intro_text <- "I am currently pursuing a master's degree in Program Evaluation and Data Analytics from Azrinoa state university, looking forward to being an aspiring data scientist and honing my data analytics skills.  I am a go-getter, and I don't mind being pushed out of my comfort zones. I am eager to learn new technologies, adapt and collaborate. With grit, dedication and pride in writing scalable, elegant code, creating simple solutions to complex data problems.
"

cat(sanitize_links(intro_text))
```



Education {data-icon=graduation-cap data-concise=true}
--------------------------------------------------------------------------------

```{r}
print_section(position_data, 'education')
```



Experience {data-icon=suitcase}
--------------------------------------------------------------------------------



```{r}
print_section(position_data, 'industry_positions')
```

<br>
<br>
<br>

Training {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------



```{r}
print_section(position_data, 'teaching_positions')
```














```{r}
if(PDF_EXPORT){
  cat("
  
Links {data-icon=link}
--------------------------------------------------------------------------------

<br>


")
  
  walk2(links, 1:length(links), function(link, index){
    print(glue('{index}. {link}'))
  })
}
```


